---
title: "Eutrophisation indicator"
author: "Laurent Dubroca <laurent.dubroca@gmail.com>"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

Rationale
http://mcc.jrc.ec.europa.eu

Descriptor 5 is defined in Annex I of the MSFD as “Human-induced eutrophication is minimised, especially adverse effects
thereof, such as losses in biodiversity, ecosystem degradation, harmful algal blooms and oxygen deficiency in bottom
waters”. Following the definition given by a dedicated MSFD Task Group Report on Descriptor 5, eutrophication is "a
process driven by enrichment of water by nutrients, especially compounds of nitrogen and/or phosphorus, leading to:
increased growth, primary production and biomass of algae; changes in the balance of organisms; and water quality
degradation. The consequences of eutrophication are undesirable if they appreciably degrade the ecosystem health and/or
the sustainable provision of goods and services."

As stated in the COM DEC [2010/477/EU pdf] “The assessment of eutrophication in marine waters needs to take into account
the assessment for coastal and transitional waters under Directive 2000/60/EC (Annex V, 1.2.3 and 1.2.4) and related
guidance (Guidance Document on the Eutrophication Assessment in the Context of European Water Policies, Document No 23.
European Commission (2009) ) in a way which ensures comparability, taking also into consideration the information and
knowledge gathered and approaches developed in the framework of regional sea conventions”.

The criteria and indicators for D5 assessment (listed below) should be synergistically considered. WFD assessments for
the transitional water should be also used for the MSFD D5 assessment, where the WFD’s Good Ecological Status should be
linked with the MSFD’s Good Environmental Status.

Eutrophisation is 


##European EEZ

```{r}
 #extraction of EEZ of the european countries
 europe<-c("Austria","Belgium","Bulgaria","Croatia","Cyprus","CzechRepublic","Denmark","Estonia","Finland","France","Germany","Greece","Hungary","Ireland","Italy","Latvia","Lithuania","Luxembourg","Malta","Netherlands","Poland","Portugal","Romania","Slovakia","Slovenia","Spain","Sweden","United
Kingdom")
 eez_europe<-eez[eez@data$Country%in%europe,]
 plot(eez_europe,title="EEZ of Europe")
```

##Chlorophyll a
```{r,eval=FALSE}
 europe_chl<-getemisdataseries("EMIS_A_CHLA","2km","2009-01","2009-12",-16.1,35.2,32.8,66)
```


Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` setion of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
