---
title: "Marine protected area analyst using EMIS/GMIS"
author: "Laurent Dubroca"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Marine protected area analyst}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

The vignette illustrates the use of the EMISR package to analyse data for a marine protected area (MPA).

# Choose your mpa

The SpatialPolygonsDataFrames `mpa1` and `mpa2` contain the marine protected areas of the world.
To select one MPA: 

```{r}
 wdpaid<-555540558
 mpa<-mpa2[mpa2@data$wdpaid==wdpaid,]
 proj4string(mpa)<-CRS("+proj=longlat +datum=WGS84")
```

Then plot it:

```{r}
 #build a terrestrial polygon around the mpa
 mappoly<-map("worldHires",fill=T,plot=FALSE,xlim=c(extent(mpa)@xmin-1,extent(mpa)@xmax+1),ylim=c(extent(mpa)@ymin-1,extent(mpa)@ymax+1))
 IDs <- sapply(strsplit(mappoly$names, ":"), function(x) x[1])
 coast<- map2SpatialPolygons(mappoly, IDs=IDs, proj4string=CRS("+proj=longlat +datum=WGS84"))
 print(paste("process localisation map"))
 #plot at global scale
 map("worldHires",col="light grey",fill=T)
 points(coordinates(mpa),cex=2,col="blue",pch="+")
 title(paste("MPA",mpa@data$wdpaid,"(",mpa@data$name,")","in",mpa@data$country),cex=.5)
 #local plot
 plot(mpa,xlim=c(extent(mpa)@xmin-1,extent(mpa)@xmax+1),ylim=c(extent(mpa)@ymin-1,extent(mpa)@ymax+1),axes=T,col="red")
 map("worldHires",add=T,col="light grey",fill=T)
 plot(mpa,add=T,col="blue")
 title(paste("MPA",mpa@data$wdpaid,"(",mpa@data$name,")","in",mpa@data$country),cex=.5)

```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` setion of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
