---
title: "Marine protected area analyst using EMIS/GMIS"
author: "Laurent Dubroca"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Marine protected area analyst}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse=TRUE,comment="#>",fig.width=6,fig.height=6)
library(EMISR)
```

The vignette illustrates the use of the EMISR package to analyse data for a marine protected area (MPA).

# Choose your mpa

The SpatialPolygonsDataFrames `mpa1` and `mpa2` contain the marine protected areas of the world.
To select one MPA: 

```{r}
 wdpaid<-555540558
 mpa<-mpa2[mpa2@data$wdpaid==wdpaid,]
 proj4string(mpa)<-CRS("+proj=longlat +datum=WGS84")
```

Then plot it:

```{r}
 #build a terrestrial polygon around the mpa
 mappoly<-map("worldHires",fill=T,plot=FALSE,xlim=c(extent(mpa)@xmin-1,extent(mpa)@xmax+1),ylim=c(extent(mpa)@ymin-1,extent(mpa)@ymax+1))
 IDs <- sapply(strsplit(mappoly$names, ":"), function(x) x[1])
 coast<- map2SpatialPolygons(mappoly, IDs=IDs, proj4string=CRS("+proj=longlat +datum=WGS84"))
 #plot at global scale
 map("worldHires",col="light grey",fill=T)
 points(coordinates(mpa),cex=2,col="blue",pch="+")
 title(paste("MPA",mpa@data$wdpaid,"(",mpa@data$name,")","in",mpa@data$country),cex=.5)
 #local plot
 plot(mpa,xlim=c(extent(mpa)@xmin-1,extent(mpa)@xmax+1),ylim=c(extent(mpa)@ymin-1,extent(mpa)@ymax+1),axes=T,col="red")
 map("worldHires",add=T,col="light grey",fill=T)
 plot(mpa,add=T,col="blue")
 title(paste("MPA",mpa@data$wdpaid,"(",mpa@data$name,")","in",mpa@data$country),cex=.5)

```

# Environmental parameters extraction and analysis

The function `mpaextract` download the requested parameter on EMIS (european waters, high spatial resolution) or GMIS
(global scale, but only available at 4 and 9 km). 
```{r,eval=FALSE}
#extraction of the MODIS sea surface temperature at 2 km between 2009 and 2012 on the Pantelleria marine protected area (Italy)
pantelleria_sst<-mpaextract("EMIS_T_SST","2km","2009-01","2012-12",555540558)
#extraction of the MODIS sea surface temperature at 2 km between 2009 and 2012 on the Pantelleria marine protected area (Italy)
pantelleria_chl<-mpaextract("EMIS_A_CHLA","2km","2009-01","2012-12",555540558)
```

Then the extracted parameters can be processed in two ways:

- graphically, some figures are elaborated (plot of the whole series, average, climatology and boxplot of the climatology). The
  function `mpaprocessplt` does this graphical processing. 

```{r,eval=TRUE}
plt<-mpaprocessplot(imgs=pantelleria_sst,mpa=pantelleria_mpa,name="EMIS_T_SST",unite="oC",logscale=FALSE)
#map of the whole series
plt[[1]]+latticeExtra::layer(sp.polygons(coast,fill="grey",col="grey"))+latticeExtra::layer(sp.polygons(pantelleria_mpa))
#map of the average SST
plt[[2]]+latticeExtra::layer(sp.polygons(coast,fill="grey",col="grey"))+latticeExtra::layer(sp.polygons(pantelleria_mpa))
#map of the climatology
plt[[3]]+latticeExtra::layer(sp.polygons(coast,fill="grey",col="grey"))+latticeExtra::layer(sp.polygons(pantelleria_mpa))
#boxplot of the climatology
plt[[4]]
```

- summary statistics for the parameter are computed thanks to the `mpaprocessstat` function. See the help of this
  function for the details of the statistical analysis done. A graphic with the time series decomposition of the
parameter values averaged on the MPA area is given.

```{r,eval=TRUE}
datstat<-mpaprocessstat(imgs=pantelleria_sst,mpa=pantelleria_mpa,name="EMIS_T_SST",unite="oC")
#the statistics
datstat[[1]]
#time series decomposition
datstat[[2]]
```

-the function `mpaprocess` calls successively the functions `mpaextract`,`mpaprocessplt` and `mpaprocessstat` and gives
all the outputs (plot and statistics) in a list.
```{r,eval=TRUE}
pltstat<-mpaprocess(name = "EMIS_A_CHLA", resolution = "4km", startdate = "2009-01", enddate = "2012-12", wdpaid = 555540558)
```

Results can be combine with more than one parameters repeating extraction and analysis changing the name of the
parameters.

